\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-11-03 doc/paper.tex
added more on modularity utility.

 The modular structure of the generated code allows for any individual
 components to be replaced with an alternative if available.  Indeed
 \fs has been intentionally designed to grow as alternative solvers
 and calculators are added and a subsequent release with an
 alternative lattice solver is already planned.{\color{red} Or Indeed
   flexible SUSY is distributed with two different main solvers, the
   two-scale solver based on the approach of \cite{} and designed for
   speed and the a lattice solver designed to solve tricky cases where
   the fixed point iteration of the two-scale approach fails to
   converge.}

@@

\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\appendix
\section{Examples}
\subsection{NMSSM}
Detailed steps to create NMSSM model file.
\subsection{\ESSM}
Detailed steps to create \ESSM model file.

>>>>

 The modular structure of the generated code allows for any individual
 components to be replaced with an alternative if available.  Indeed
 \fs has been intentionally designed to grow as alternative solvers
 and calculators are added and a subsequent release with an
 alternative lattice solver is already planned.{\color{red} Or Indeed
   flexible SUSY is distributed with two different main solvers, the
   two-scale solver based on the approach of \cite{} and designed for
   speed and the a lattice solver designed to solve tricky cases where
   the fixed point iteration of the two-scale approach fails to
   converge.}  In addition if one already has an existing code for
 some other purpose and simply wishes to improve upon this by adding,
 e.g, new RGEs or self energies the modular fraework makes this fairly
 straightward{\color{red} Is this true?  because it should be...}

@@

\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\section{Using individual modules in your own code}
\appendix
\section{Examples}
\subsection{NMSSM}
Detailed steps to create NMSSM model file.
\subsection{\ESSM}
Detailed steps to create \ESSM model file.
